### 2014-11-08 tex/precise.tex

The rewrite rules for check the equals true and equals false when
comparing two references in the symbolic summary heap is shown
in~\figref{fig:eqs}(a). First the equals reference true rewrite rule
returns true if two references $r_0$ and $r_1$ are equal. In GSE this
is a simple comparision of object refrences. In the symbolic summary
heap, however, there we campare sets of constraint location pairs for
each reference. We construct three sets of constraints (i)
$\Phi_\alpha$ constains combinations of constraints ($\phi_0 \wedge
\phi_1$) from $r_0$ and $r_1$

>>>>

The rewrite rules for check the equals true and equals false when
comparing two references in the symbolic summary heap is shown
in~\figref{fig:eqs}(a). First the equals reference true rewrite rule
returns true if two references $r_0$ and $r_1$ are equal. In GSE this
is a simple comparision of object refrences. In the symbolic summary
heap, however, there we campare sets of constraint location pairs for
each reference. We construct three sets of constraints (i) In order to check whether 
there are locations, $l$ in the heap such that under some constraints $\phi_0$ references $r_0$ and $r_1$
$\Phi_\alpha$ constains combinations of constraints ($\phi_0 \wedge
\phi_1$) from $r_0$ and $r_1$
